Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-15 writeup/rocha_etal.tex
Adds link to repo in the acknowledgement

\begin{acknowledgments}
 William R. Young provided helpful feedback on the first draft. We thank the MITgcm community and our colleagues at the NASA Advanced
Supercomputing (NAS) Division for their awesome support.
This research was funded by NSF (OCE1357047) and NASA (NNX13AE44G,NNX13AE85G,NNX16AH67G).
The LLC output can be obtained from the ECCO project (\texttt{http://ecco2.org/llc$\_$hires}). The altimeter products were produced by Ssalto/Duacs
and distributed by Aviso, with support from CNES (\texttt{http://www.aviso.altimetry.fr/duacs/}).
\end{acknowledgments}

>>>>

\begin{acknowledgments}
 William R. Young provided helpful feedback on the first draft. We thank the MITgcm community and our colleagues at the NASA Advanced
Supercomputing (NAS) Division for their awesome support.
This research was funded by NSF (OCE1357047) and NASA (NNX13AE44G,NNX13AE85G,NNX16AH67G).
The LLC output can be obtained from the ECCO project (\texttt{http://ecco2.org/llc$\_$hires}). The altimeter products were produced by Ssalto/Duacs
and distributed by AVISO, with support from CNES (\texttt{http://www.aviso.altimetry.fr/duacs/}).
Codes and output files are available online at the project repository
 \texttt{https://github.com/crocha700/UpperOceanSeasonality}.
\end{acknowledgments}
